Minimizing post-shock forecasting error through aggregation of outside information

### 2021-01-25 Revision/list.tex
updated referee report

\response{We include another example in which we forecast the stock price of Apple Inc. after the latest release of their MacBook product in 2020. This example is included in Section 5.2 of the revised manuscript. In this example, the donor pool constructed includes three past time series of  Apple inc.'s stock price surrounding previous releases of the MacBook which occurred over the past three years. In this example, the shock is with precedent and our method is expected to work well. This is because Apple Inc. is a well-established company that did not revolutionize the Macbook. Our adjusted forecast performs very well in this setting, as expected. This example is representative for applying our methods to the time series that are to experience a shock that is with some precedent in the past. In contrast, the example of Conoco Phillips is without precedent. In the past, Conoco Phillips  did not experience oil supply shock and financial crisis shock caused by a pandemic. In this example, our method is better than the original forecast though it cannot fully recover the stock price. We hope that the addition of the Apple example helps to generate confidence in our approach.}

@@

\response{Our methodology requires that a practitioner can choose a suitable donor pool of candidate shock-effects. If this cannot be done, then the methodology may not work well. Practitioners can use qualitative and quantitative information to inform their decisions about which time series inform the donor pool. Consider our Conoco Phillips example. On March 9th 2020, Conoco Phillips was expected to experience a negative shock in the midst of the  COVID-19 pandemic and an oil supply shock. While the COVID-19 pandemic is unprecedented, several economic measurements surrounding March 9th 2020 resembled those in the days of the 2008 financial crises. On the other hand, the oil supply shock had precedent. As a result, we selected the shocks in the past corresponding to the 2008 financial crisis and a past 2014 oil supply shock.} \\

>>>>

\response{We include another example in which we forecast the stock price of Apple Inc. after the latest release of their MacBook product in 2020. This example is included in Section 5.2 of the revised manuscript. In this example, the donor pool includes three past time series of  Apple inc.'s stock price surrounding previous releases of the MacBook. In this example, the shock is with precedent and our method is expected to work well. This is because Apple Inc. is a well-established company that did not revolutionize the MacBook product in their last three releases. Apple Inc. mostly focused on upgrading the hardware in the MacBook, this same is true for the latest release. Our adjusted forecast performs very well in this setting, as expected. This example is representative for a class of problems involving shocks that are very similar to those in the past. In contrast, the example of Conoco Phillips is without precedent. In the past, Conoco Phillips  did not experience a financial crisis shock caused by a pandemic supplemented with an oil price shock. In the Conoco Phillips example, our method is better than the original forecast, although we do not fully recover the yet to be observed stock price. We hope that the addition of the Apple example helps to generate confidence in our approach.}

@@

\response{Our methodology requires that a practitioner can choose a suitable donor pool of candidate shock-effects. If this cannot be done, then the methodology may not work well. Practitioners can use qualitative and quantitative information to inform their decisions about which time series are included in the donor pool. Consider our Conoco Phillips example. On March 9th 2020, Conoco Phillips was expected to experience a negative shock in the midst of the  COVID-19 pandemic and an oil supply shock. While the COVID-19 pandemic is unprecedented, several economic measurements surrounding March 9th 2020 resembled those in the days of the 2008 financial crises. On the other hand, the oil supply shock had precedent. As a result, we selected the shocks in the past corresponding to the 2008 financial crisis and a past 2014 oil supply shock.} \\

### 2021-01-25 Revision/manuscript.tex
updated referee report

Construction of the donor pool is a critical step that directly matters in prediction. In our model, shocks from candidate time series in the donor pool, together with the shock in the time series of interest, should come from a family of distributions that allow for  varying variances and  varying means that are linear functions of common covariates. Remark \ref{remark1} shows that common covariates are not restrictive with structural zero in coefficients. However, it is difficult to verify such assumption or structure in practice. In principle, one should select identities that come from a common population, which is also the one  the identity under study come from, as candidates in donor pool. This selection criterion is often adopted in the literature of comparative case studies. For example, \citet{card1990impact} used a set of cities in southern U.S. to estimate the effect of 1980 Mariel Boatlift on the Miami labor market. \citet{abadie2003economic} utilized a donor pool of two Spanish regions to approximate the effect of terrorism on  the economic growth of Baseque Country. To estimate the effect of Proposition 99, a large tabacco control program in California  in 1988, on the annual per-capita cigarette sales of 2000, \cite{abadie2010synthetic} constructed a donor pool consisting of US states, which did not implement \emph{any} large-scale tobacco control program during their sampling period. Common features of those studies are that they all carefully constructed the donor pool and discarded any suspicious outliers.

>>>>

Construction of the donor pool is a critical step that directly matters in prediction. In our model, shocks from candidate time series in the donor pool, together with the shock in the time series of interest, should come from a family of distributions that allow for  varying variances and  varying means that are linear functions of common covariates. Remark \ref{remark1} shows that common covariates are not restrictive with structural zero in coefficients. However, it is difficult to verify such assumption or structure in practice. In principle, one should select individuals that come from a common population, the same populationas the individual under study, to form the donor pool. This selection criterion is often adopted in the literature of comparative case studies. For example, \citet{card1990impact} used a set of cities in southern U.S. to estimate the effect of 1980 Mariel Boatlift on the Miami labor market. \citet{abadie2003economic} utilized a donor pool of two Spanish regions to approximate the effect of terrorism on  the economic growth of Baseque Country. To estimate the effect of Proposition 99, a large tobacco control program in California  in 1988, on the annual per-capita cigarette sales of 2000, \cite{abadie2010synthetic} constructed a donor pool consisting of US states, which did not implement \emph{any} large-scale tobacco control program during their sampling period. Common features of those studies are that they all carefully constructed the donor pool and discarded any suspicious outliers.
